%------------------------
% LaTeX CV for Guangrui Fan
% Based on Northeastern University Faculty Template
% Generated: January 2026
% 
% Compile with: pdflatex CV_Guangrui_Fan.tex
%------------------------

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{geometry}
\geometry{a4paper, margin=0.85in}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{xcolor}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue!70!black,
    urlcolor=blue!70!black,
    citecolor=blue!70!black
}

% Formatting
\setlist{noitemsep}
\setlength{\parindent}{0pt}
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip}
\newenvironment{subs}
  {\adjustwidth{2em}{0pt}}
  {\endadjustwidth}

% Custom commands
\newcommand{\pubitem}[1]{\item #1}
\newcommand{\cvlabel}[1]{\textbf{#1}}

%-------------------------------------------------------------------------------
% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
    \textbf{\Large GUANGRUI FAN}\\[3pt]
    \textbf{Curriculum Vitae}\\[2pt]
    Date of Birth: July 6, 1992\\[2pt]
    \begin{tabularx}{0.96\textwidth}{@{}X X@{}}
      \faMapMarker*~Taiyuan, Shanxi, China &
      \faPhone~+86 13387574446 \\
      \faEnvelope~\href{mailto:gerryfan2022@gmail.com}{gerryfan2022@gmail.com} &
      \faGlobe~\href{https://gerryfan0706.github.io}{gerryfan0706.github.io} \\
      \faOrcid~\href{https://orcid.org/0009-0001-8570-1636}{0009-0001-8570-1636} &
      \faGithub~\href{https://github.com/gerryfan0706}{github.com/gerryfan0706} \\
    \end{tabularx}
\end{center}

%------------------------
% Research Interests
\section*{RESEARCH INTERESTS}

\textbf{Human-Centered Artificial Intelligence (HCAI)} with a focus on:
\begin{itemize}[leftmargin=*]
    \item \textbf{AI in Education}: cognitive scaffolding and offloading in AI-assisted programming education.
    \item \textbf{AI-Mediated Communication \& Trust}: authenticity, trust, privacy, and attribution in AI-assisted communication/content creation.
    \item \textbf{Intelligent Transportation}: GNN-based spatiotemporal traffic prediction and fairness.
    \item \textbf{AI for Social Good}: mental health support and algorithmic fairness.
\end{itemize}
\noindent\textbf{Keywords:} Human-Centered AI; HCI; LLMs; Graph Neural Networks; Social Computing; Fairness.

%------------------------
\section*{RESEARCH HIGHLIGHTS}
\begin{itemize}[leftmargin=*]
    \item \textbf{Representative publications:} 7 CCF A conference papers and 6 Chinese Academy of Sciences (CAS) Q1 Top journal papers, all as first or corresponding author; including 3 papers accepted to CHI 2026, with one receiving an ACM CHI 2026 Honourable Mention Award.
    \item \textbf{ESI Highly Cited Paper (2025):} \textit{International Journal of STEM Education}.
    \item \textbf{Service:} Program Committee member (WWW 2026, Web4Good); Reviewer for CHI 2026 and multiple SCI/SSCI Q1 journals.
\end{itemize}

%------------------------
% Education Section
\section*{EDUCATION}

\noindent
\textbf{Ph.D. in Computer Science} \hfill September 2022 -- March 2026 (Expected) \\
Universiti Malaya (QS 58), Kuala Lumpur, Malaysia \\
Research Focus: Human-Centered AI, Human-AI Interaction, Intelligent Transportation \\

\noindent
\textbf{M.S. in Software Engineering} \hfill September 2014 -- February 2018 \\
Shanghai Jiao Tong University, Shanghai, China (School of Software) \\
\textit{Direct Admission (Recommended without Entrance Exam)} \\

\noindent
\textbf{B.S. in Digital Media Technology} \hfill September 2010 -- June 2014 \\
Huazhong University of Science and Technology, Wuhan, China (School of Software)

%------------------------
% Employment Section
\section*{EMPLOYMENT HISTORY}

\noindent
\textbf{Lecturer} \hfill June 2018 -- Present \\
School of Computer Science and Technology \\
Taiyuan University of Science and Technology, Taiyuan, China

%------------------------
% Publications Section
\section*{PUBLICATIONS\footnotemark[1]}
\footnotetext[1]{\(^*\) First Author; \(^\dag\) Corresponding Author.}

\subsection*{Peer-Reviewed Conference Papers}

\subsubsection*{CCF A}

\begin{enumerate}[label={[C\arabic*]}]
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., et al. (2026). Is It Still You? Attributing Authorship and Authenticity in AI-Assisted Romantic Communication. In \textit{CHI 2026}. \textbf{CCF A}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., et al. (2026). When Help Hurts: Verification Load and Fatigue with AI Coding Assistants. In \textit{CHI 2026}. \textbf{CCF A}; \textbf{ACM CHI 2026 Honourable Mention Award}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., et al. (2026). Co-Adaptive Eco-Nudging: A Privacy-Preserving Contextual Bandit with User-Taught Preferences. In \textit{CHI 2026}. \textbf{CCF A}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., Pan, L., et al. (2026). Multi-LLM Persona Generation for Virtual Focus Groups in Software Engineering. In \textit{FSE 2026}. \textbf{CCF A}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., Sabri, A.Q.M., \& Pan, L. (2026). Audit-of-Audits for the Web: Bayesian Meta-Evaluation that Yields Interval-Valued, Threshold-Aligned Fairness Claims. In \textit{WWW 2026}. \textbf{CCF A}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., \& Pan, L. (2026). Mind the Gap: Predicting, Explaining and Reducing Time-to-First-Comment (Reply Gap) in Online Mental-Health Communities. In \textit{AAAI 2026}. \textbf{CCF A}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., Pan, L., \& Huang, Y. (2025). Creative Momentum Transfer: How Timing and Labeling of AI Suggestions Shape Iterative Human Ideation. In \textit{IJCAI 2025}. \textbf{CCF A}}
\end{enumerate}

\subsubsection*{CCF B}

\begin{enumerate}[label={[C\arabic*]}, resume]
    \pubitem{\textbf{Fan, G.}$^*$, Pan, L., Zhang, M., \& Zhao, M. (2026). LePER: Label-Free Edge Polarity Reweighting for Heterophily. In \textit{ICASSP 2026}. \textbf{CCF B}}
    
    \pubitem{\textbf{Fan, G.}$^*$, \& Liu, D. (2025). When Machines Speak with Feeling: Investigating Emotional Prosody, Authenticity, and Trust in AI vs. Human Voices. In \textit{CogSci 2025}. \textbf{CCF B}}
    
    \pubitem{\textbf{Fan, G.}$^*$, \& Liu, D. (2025). Co-Constructing Meaning with Large Language Models: A Longitudinal Analysis of Human-AI Dialogues in Emotional Support Contexts. In \textit{CogSci 2025}. \textbf{CCF B}}
\end{enumerate}

\subsubsection*{CCF C}

\begin{enumerate}[label={[C\arabic*]}, resume]
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., Pan, L., \& Huang, Y. (2025). Mapping Override Behavior: Investigating Why and How Artists Reject AI Suggestions in Collaborative Creation. In \textit{IJCNN 2025}. \textbf{CCF C}}
    
    \pubitem{\textbf{Fan, G.}$^*$ (2025). DocPINN: A Neural PDE-Based Framework for Document Image Dewarping. In \textit{ICDAR 2025}. \textbf{CCF C}}
\end{enumerate}

\subsection*{Peer-Reviewed Journal Articles}

\subsubsection*{SCI Q1 Top Journals}

\begin{enumerate}[label={[J\arabic*]}]
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., Zhang R., \& Pan, L. (2025). The impact of AI-assisted pair programming on student motivation, programming anxiety, collaborative learning, and programming performance. \textit{International Journal of STEM Education, 12}(1), 16. \textbf{SCI Q1 Top, ESI Highly Cited}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., et al. (2026). Tool, Tutor, or Crutch?: A Grounded Theory of Cognitive Scaffolding and Offloading in AI-Assisted Programming Education. \textit{International Journal of STEM Education}. (In Press) \textbf{SCI Q1 Top}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Sabri, A.Q.M., Rahman, S.S.A., \& Pan, L. (2025). DynaKey-GNN: An efficient dynamic key-node multi-graph neural network for spatio-temporal traffic flow forecasting. \textit{Engineering Applications of Artificial Intelligence, 159}, 111757. \textbf{SCI Q1 Top}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Sabri, A.Q.M., Rahman, S.S.A., Pan, L., \& Rahardja, S. (2025). Emerging Trends in Graph Neural Networks for Traffic Flow Prediction: A Survey. \textit{Archives of Computational Methods in Engineering}, 1--45. \textbf{SCI Q1 Top}}
    
    \pubitem{Liu, D., \& \textbf{Fan, G.}$^\dag$ (2026). Governing Modesty: Platformed Urban Gaze and Rural Chinese Housewives on Douyin. \textit{Journal of Rural Studies}. \textbf{SCI Q1 Top}}
    
    \pubitem{Liu, D., \& \textbf{Fan, G.}$^\dag$ (2025). Digital duality: negotiating tradition, modernity, and identity among rural housewife Douyin creators in China. \textit{Information, Communication \& Society}, 1--18. \textbf{SCI Q1 Top}}
\end{enumerate}

\subsubsection*{CCF B / Other SCI Journals}

\begin{enumerate}[label={[J\arabic*]}, resume]
    \pubitem{\textbf{Fan, G.}$^*$, Liu, D., \& Huang, Y. (2025). Skim or Swim? Investigating AI-Generated Summaries, Trust, and Comprehension in Chinese Mobile Reading. \textit{International Journal of Human--Computer Interaction}, 1--22. \textbf{CCF B}}
    
    \pubitem{Zhao, R., Quan, Y., \& \textbf{Fan, G.}$^\dag$ (2025). Optimizing Operating Room Scheduling Through Multi-Level Learning and Column Generation. \textit{Health Care Management Science}. \textbf{SCI Q3}}
    
    \pubitem{\textbf{Fan, G.}$^*$, Liu, A., \& Zhang, C. (2025). ContrastLOS: A Graph-Based Deep Learning Model With Contrastive Pre-Training for Improved ICU Length-of-Stay Prediction. \textit{IEEE Access}. \textbf{SCI Q3}}
\end{enumerate}

%------------------------
% Honors and Awards
\section*{HONORS \& AWARDS}

\begin{itemize}[leftmargin=*]
    \item \textbf{ACM CHI 2026 Honourable Mention Award} -- \textit{When Help Hurts: Verification Load and Fatigue with AI Coding Assistants}
    \item \textbf{ESI Highly Cited Paper} (2025) -- \textit{International Journal of STEM Education}
    \item \textbf{Most Cited Article (Past Two Years)} -- \textit{International Journal of STEM Education}
    \item \textbf{Most Popular Article (Rank 1, Past 9 Months)} -- \textit{International Journal of STEM Education}
    \item \textbf{First-Class Paper Award \& Best Presentation Award} (July 2025) -- The 9th China Computer Practice Education Conference (CPEC 2025)
\end{itemize}

%------------------------
% Grants Section
\section*{GRANTS \& RESEARCH PROJECTS}

\begin{itemize}[leftmargin=*, topsep=0.2ex, itemsep=0.2ex]
    \item \cvlabel{Shanxi Basic Research Program (Participant)}: Multi-Agent Parallel Simulation Model for Large-Scale Complex Systems Based on Mesoscale. \;\cvlabel{Project No.:} 202203021221145
    \item \cvlabel{Shanxi Higher Education Teaching Reform Project (Team Member, 2025)}: Deepening Undergraduate Teaching Evaluation Reform: AI-Empowered Classroom Quality Assessment. \;\cvlabel{Project No.:} J20250145
\end{itemize}

%------------------------
% Teaching Section
\section*{TEACHING}

\noindent
\textbf{Courses Taught:} Java Web Development, Oracle Database Management, IoT RFID Principles and Technology, Computer Graphics, Computer Animation Principles

\noindent
\textbf{Student Supervision:} Undergraduate thesis projects in AI and software engineering

%------------------------
% Service Section
\section*{PROFESSIONAL SERVICE}

\subsection*{Program Committee Member}
\begin{itemize}[leftmargin=*]
    \item \textbf{The Web Conference (WWW) 2026} -- Special Track: Web4Good (CCF A)
\end{itemize}

\subsection*{Journal \& Conference Reviewer}
\begin{itemize}[leftmargin=*]
    \item \textbf{CHI 2026} -- ACM Conference on Human Factors in Computing Systems (CCF A)
    \item \textbf{Engineering Applications of Artificial Intelligence} (EAAI, SCI Q1 Top)
    \item \textbf{International Journal of STEM Education} (SCI Q1 Top)
    \item \textbf{Information, Communication \& Society} (SSCI Q1 Top)
\end{itemize}

%------------------------
% Footer
\vfill
\begin{center}
    \small Last Updated: March 2026
\end{center}

\end{document}

%-------------------------------------------------------------------------------
% Compilation Instructions:
%-------------------------------------------------------------------------------
% 1. Compile with pdfLaTeX:
%    pdflatex CV_Guangrui_Fan.tex
%
% 2. Overleaf:
%    Menu -> Compiler -> pdfLaTeX
%-------------------------------------------------------------------------------
